---
title: "homework_4_kanutala_santosh"
author: "Santosh Kanutala"
date: "7/1/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## **My Github repository for my assignments can be found at below URL:       (https://github.com/santumagic/compscix-415-2assignments.git)**

```{r load_packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(mdsr)
library(nycflights13)
```
## Section 5.6.7: #2, #4 and #6 only. Extra Credit: Do #5

### **QUESTION 2:**
```{r question_5.6.7_2, message=FALSE, warning=FALSE}
# First lets find the not cancelled flights.
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))

# given code for not_cancelled %>% count(dest)
not_cancelled %>%
  count(dest)

# new code for not_cancelled %>% count(dest) by group by and summarise
not_cancelled %>%
  group_by(dest) %>%
  summarise(n = n())

# given code for not_cancelled %>% count(tailnum, wt = distance)
not_cancelled %>%
  count(tailnum, wt = distance)

# new code for not_cancelled %>% count(tailnum, wt = distance) group by and summarise
not_cancelled %>%
  group_by(tailnum) %>%
  summarize(n = sum(distance, na.rm = TRUE))
```

### **QUESTION 4:**
```{r question_5.6.7_4, message=FALSE, warning=FALSE}
# number of cancelled flights per day
(cancelled_flights <- flights %>%
  filter(is.na(dep_time)) %>%
  count(day))

# proportion of day cancelled flights vs aerage delays
(cancelled_flights <- flights %>%
  group_by(day) %>%
  summarize(prop_cancelled = sum(is.na(dep_time)) / n(),
            avg_delay = mean(dep_time, na.rm = TRUE)))

# plot for the relationship
ggplot(cancelled_flights, aes(x = prop_cancelled, y = avg_delay)) +
  geom_point() +
  geom_smooth()

```

### **QUESTION 6:**
```{r question_5.6.7_6, message=FALSE, warning=FALSE}

```
### **ANSWER 6:**

sort argument will sort the elements of count () in the decending order. After the results are extracted, we can use the sort to arrange the values.

## Section 10.5: #1, #2, #3 and #6 only. 

### **QUESTION 2:**
```{r question_10.5_1, message=FALSE, warning=FALSE}
# mtcars as a data frame
print(mtcars)

# mtcars as a tibble
print(as_tibble(mtcars))
```

When we print a dataframe whole records will be printed where as with the tibble only top rows will be printed and  
the columns and widths are adjusted to fit the screen resolution.

### **QUESTION 2:**
```{r question_10.5_2, message=FALSE, warning=FALSE}
# with a data frame
df <- data_frame(abc = 1, xyz = 'a')
df
df$x
df[, "xyz"]
df[, c("abc", "xyz")]

# with a tibble
df <- tibble(abc = 1, xyz = "a")
df
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```
By using $ we can only extract by names. tibbles are much strictier and they alert us when we are trying to pull a column which never existed.

### **QUESTION 3:**
```{r question_10.5_3, message=FALSE, warning=FALSE}
var <- "mpg"
```
### **ANSWER:**
We can extract the refernce variable by uisng double square brackets like df[[var]]

### **QUESTION 6:**
```{r question_10.5_6, message=FALSE, warning=FALSE}
?tibble
```
### **ANSWER:**
```{r}
getOption("tibble.max_extra_cols")
```

## Section 12.3.3: #2, #3 and #4 only. 

### **QUESTION 2:**
```{r question_12.3.3_2, message=FALSE, warning=FALSE}

# table4a %>%
  # gather(1999, 2000, key = "year", value = "cases") # commented out as it is failing and need to ask instructor
```
### **ANSWER:**
we need to add the quotes around 1999 & 2000 otherwise 1999 & 2000 are treated as columns in the data frame. Below is the modified code.
```{r question_12.3.3_2_ans, message=FALSE, warning=FALSE}
table4a %>%
  gather('1999', '2000', key = "year", value = "cases")
```

### **QUESTION 3:**
```{r question_12.3.3_3, message=FALSE, warning=FALSE}
# given code 
 people <- tribble(
   ~name,             ~key,    ~value,
  #-----------------|--------|------
  "Phillip Woods",   "age",       45,
  "Phillip Woods",   "height",   186,
  "Phillip Woods",   "age",       50,
  "Jessica Cordero", "age",       37,
  "Jessica Cordero", "height",   156
)

# Spreading the above tibble
# spread(people, key, value) # commented out as it is failing and need to ask instructor
```
### **ANSWER:**
Duplicates are identified. In otherwords Phillip has two age records. In this case we can add another column related to the row identifier like the people_id then the issue will be resolved. Below is the code for the same.
```{r}
people$people_id <- c(1, 1, 2, 1, 1)
people # display the modified tibble
spread(people, key, value) # spread the tibble

```

### **QUESTION 4:**
```{r question_12.3.3_4, message=FALSE, warning=FALSE}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)
```
### **ANSWER:**

By lokking at above tibble, we can observe that there is a missing value. So we can use gather() and add na.rm = TRUE to remove the value NA. Below is the gathered tibble with variables, pregnant, gender, count.
```{r question_12.3.3_4_ans, message=FALSE, warning=FALSE}
preg %>%
  gather(key = 'gender', value = 'value', c(2:3), na.rm = TRUE)
```

## Section 12.4.3: #1 and #2 only. 

### **QUESTION 1:**
```{r question_12.4.3_1, message=FALSE, warning=FALSE}
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"))

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"))

# help on the separate
?separate
```
### **ANSWER:**
'extra' argument controls what happens when there are too many pieces. It can drop extra values by warning or without warning or it can merge.  
'fill' controls what happens when there are not enough piece by filling the missing values from right or left with or without a warning.

```{r question_12.4.3_1_ans, message=FALSE, warning=FALSE}
# using extra = "drop"
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "drop")

# using extra = "merge"
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "merge")

# using fill = "right"
tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill = "right")

# using fill = "left"
tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill = "left")
```

### **QUESTION 2:**
Both unite() and separate() have a remove argument. What does it do? Why would you set it to FALSE?
  
### **ANSWER:**
remove argument will remove the original input columns from the output. If we change it to FALSE then the original columns are retained in the output.






