---
title: "homework_4_kanutala_santosh"
author: "Santosh Kanutala"
date: "7/1/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## **My Github repository for my assignments can be found at below URL:       (https://github.com/santumagic/compscix-415-2assignments.git)**

```{r load_packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(mdsr)
library(nycflights13)
```
## Section 5.6.7: #2, #4 and #6 only. Extra Credit: Do #5

### **QUESTION 2:**
```{r question_5.6.7_2, message=FALSE, warning=FALSE}
# First lets find the not cancelled flights.
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))

# given code for not_cancelled %>% count(dest)
not_cancelled %>%
  count(dest)

# new code for not_cancelled %>% count(dest) by group by and summarise
not_cancelled %>%
  group_by(dest) %>%
  summarise(n = n())

# given code for not_cancelled %>% count(tailnum, wt = distance)
not_cancelled %>%
  count(tailnum, wt = distance)

# new code for not_cancelled %>% count(tailnum, wt = distance) group by and summarise
not_cancelled %>%
  group_by(tailnum) %>%
  summarize(n = sum(distance, na.rm = TRUE))
```

### **QUESTION 4:**
```{r question_5.6.7_4, message=FALSE, warning=FALSE}
# number of cancelled flights per day
(cancelled_flights <- flights %>%
  filter(is.na(dep_time)) %>%
  count(day))

# proportion of day cancelled flights vs aerage delays
(cancelled_flights <- flights %>%
  group_by(day) %>%
  summarize(prop_cancelled = sum(is.na(dep_time)) / n(),
            avg_delay = mean(dep_time, na.rm = TRUE)))

# plot for the relationship
ggplot(cancelled_flights, aes(x = prop_cancelled, y = avg_delay)) +
  geom_point() +
  geom_smooth()

```

### **QUESTION 6:**
```{r question_5.6.7_6, message=FALSE, warning=FALSE}

```
### **ANSWER 6:**

sort argument will sort the elements of count () in the decending order. After the results are extracted, we can use the sort to arrange the values.

## Section 10.5: #1, #2, #3 and #6 only. 

### **QUESTION 2:**
```{r question_10.5_1, message=FALSE, warning=FALSE}
# mtcars as a data frame
print(mtcars)

# mtcars as a tibble
print(as_tibble(mtcars))
```

When we print a dataframe whole records will be printed where as with the tibble only top rows will be printed and  
the columns and widths are adjusted to fit the screen resolution.

### **QUESTION 2:**
```{r question_10.5_2, message=FALSE, warning=FALSE}
# with a data frame
df <- data_frame(abc = 1, xyz = 'a')
df
df$x
df[, "xyz"]
df[, c("abc", "xyz")]

# with a tibble
df <- tibble(abc = 1, xyz = "a")
df
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```
By using $ we can only extract by names. tibbles are much strictier and they alert us when we are trying to pull a column which never existed.

### **QUESTION 3:**
```{r question_10.5_3, message=FALSE, warning=FALSE}
var <- "mpg"
```
### **ANSWER:**
We can extract the refernce variable by uisng double square brackets like df[[var]]

### **QUESTION 6:**
```{r question_10.5_6, message=FALSE, warning=FALSE}
?tibble
```
### **ANSWER:**
```{r}
getOption("tibble.max_extra_cols")
```

## Section 12.3.3: #2, #3 and #4 only. 

### **QUESTION 2:**
```{r question_12.3.3_2, message=FALSE, warning=FALSE}

# table4a %>%
  # gather(1999, 2000, key = "year", value = "cases") # commented out as it is failing and need to ask instructor
```
### **ANSWER:**
we need to add the quotes around 1999 & 2000 otherwise 1999 & 2000 are treated as columns in the data frame. Below is the modified code.
```{r question_12.3.3_2_ans, message=FALSE, warning=FALSE}
table4a %>%
  gather('1999', '2000', key = "year", value = "cases")
```

### **QUESTION 3:**
```{r question_12.3.3_3, message=FALSE, warning=FALSE}
# given code 
 people <- tribble(
   ~name,             ~key,    ~value,
  #-----------------|--------|------
  "Phillip Woods",   "age",       45,
  "Phillip Woods",   "height",   186,
  "Phillip Woods",   "age",       50,
  "Jessica Cordero", "age",       37,
  "Jessica Cordero", "height",   156
)

# Spreading the above tibble
# spread(people, key, value) # commented out as it is failing and need to ask instructor
```
### **ANSWER:**
Duplicates are identified. In otherwords Phillip has two age records. In this case we can add another column related to the row identifier like the people_id then the issue will be resolved. Below is the code for the same.
```{r}
people$people_id <- c(1, 1, 2, 1, 1)
people # display the modified tibble
spread(people, key, value) # spread the tibble

```














