---
title: \vspace{.5in}"__COMPSCIX 415.2 Homework 6__"
author: "__Santosh Kanutala__"
date: "7/17/2018"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    highlight: tango
  html_document:
    highlight: tango
    number_sections: no
    theme: readable
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\newpage
## <u>Github location</u>
My homework assignments can be found at   https://github.com/santumagic/compscix-415-2assignments.git

## <u>Exercise 1</u>
### Question: 1
```{r Ex_1_Q1, message=FALSE, warning=FALSE}
# Load the required packages
library(tidyverse)
library(mdsr)
library(mosaicData)
# glimpse the given dataset
glimpse(Whickham)
```
**Answer:**  
Below are the three variables from the Whickham dataset.  

+ outcome  
+ smoker  
+ age

### Question: 2
```{r Ex_1_Q2, message=FALSE, warning=FALSE}
```
**Answer:**  
There are 1314 observations. Each observation represents a person. The data set indicates if the individual is a smoker or not, current age an individual, and if the individual is alive or dead.

### Question: 3
```{r Ex_1_Q3, message=FALSE, warning=FALSE}
library(mosaicData)
library(tidyverse)
Whickham %>% count( smoker , outcome )
```
**Answer:**  
By looking at the above table, it is difficult to conclude anything, so I calculate the proportions first by using the below code.

```{r}
Whickham_proportions <- Whickham %>% group_by(smoker,outcome) %>% 
  summarize(n = n()) %>% 
  mutate ( prop = n/sum(n))
 Whickham_proportions 
```

By looking at the above proportions it is observed that, 31.4 % of non smokers are dead and 23.8 % of smokers are dead which means more healthy people are dead. So there must be other reasons for deaths or data might be wrong. So the data doesn't make any sense.

### Question: 4
```{r Ex_1_Q4, message=FALSE, warning=FALSE, fig.align='center'}
# creating the age groups column
Whickham_factor <- Whickham %>% mutate (category = 
                                          factor (
case_when(age <= 44 ~ "age <= 44", age > 44 & age <= 64 ~ "age > 44 & age <= 64", 
          age > 64 ~ "age > 64")))

head(Whickham_factor) # display the top rows of the result dataset

# reorganize the data by grouping,summarise the data and finding the proportions
Whickham_cat <- Whickham_factor %>%
group_by(category,smoker,outcome) %>% summarise( n = n()) %>%
mutate (proportion = n/sum(n))

head(Whickham_cat) # display the top rows of the result dataset

# create the visualization with the above result set and facet on age categories
Whickham_cat %>% 
ggplot() + 
  geom_bar(aes(x = smoker, y = proportion, fill = outcome, label = round(proportion,2)), 
           stat = 'identity', position = 'fill') +
  labs(x = 'smoker', y = 'outcome', fill = 'proportion',
       title = 'Smoker status by age category') +
  facet_grid(~ category) +
  theme_bw()
```
**Answer:**  
From the above dataset it is observed that untill the age of 44, non-smokers have only a 1% advantage compared to smokers, but this gap increases dramatically between the ages 44 & 64 where 6% more non-smokers are alive than smokers. Beyond 64 year of age, the difference drops to 3% with non-smokers still being alive more often than smokers.

\newpage
## <u>Exercise 2</u>
### Question: 1
```{r Ex_2_Q1, message=FALSE, warning=FALSE, fig.align='center'}
# given sample code
library(tidyverse)
n <- 10000
# look at ?rgamma to read about this function
gamma_samp <- tibble(x = rgamma(n, shape = 1, scale = 2))
gamma_samp

# histogram for the above sample gamma
ggplot(data = gamma_samp) + 
  geom_histogram(aes(x=x), bins=100) + 
  theme_bw()

```

### Question: 2
```{r Ex_2_Q2, message=FALSE, warning=FALSE}
# finding mean
sprintf ("Mean = %f",sapply(gamma_samp, mean, na.rm = TRUE))

# finding standard deviation
sprintf ("Standard deviation = %f", sapply(gamma_samp, sd, na.rm = TRUE))
```
### Question: 3
```{r Ex_2_Q3, message=FALSE, warning=FALSE, fig.align='center'}
# sample of size n = 30
sample_30 <- gamma_samp %>% sample_n(30, replace = TRUE) 

# finding mean
sprintf("Mean = %f", sapply(sample_30, mean, na.rm = TRUE))

# finding standard deviation
sprintf ("Standard deviation = %f", sapply(sample_30, sd, na.rm = TRUE))

# Plot the histogram
ggplot(data =sample_30, mapping = aes(x=x)) + 
  geom_histogram(bins=5) + 
  theme_bw()
```

### Question: 4
```{r Ex_2_Q4, message=FALSE, warning=FALSE, fig.align='center'}
mean_samp <- rep(NA, 10000) 

mean_sd <- rep(NA, 10000)
for (i in 1:10000) {
g_samp <- gamma_samp %>% 
  sample_n(30, replace = TRUE) 
mean_samp[i] <- mean(g_samp$x)
mean_sd[i] <- sd(g_samp$x)
}
# tibbles for mean_samp and mead_sd
mean_samp_tibble <- tibble(mean_samp)
mean_sd_tibble <- tibble(mean_sd)
mean_dist <- bind_cols(mean_samp_tibble,mean_sd_tibble)

# display the sample of final vector
head(mean_dist)
```
### Question: 5
```{r Ex_2_Q5, message=FALSE, warning=FALSE, fig.align='center'}
# plot for the means
ggplot(data = mean_dist, mapping = aes(x=mean_samp_tibble)) + 
  geom_histogram(bins=100) +
  theme_bw()
```
### Question: 6
```{r Ex_2_Q6, message=FALSE, warning=FALSE, fig.align='center'}

# from the code of Question 4 : below are sample of the standard deviations of the population
head(mean_sd_tibble)

# plot for the standard deviation
ggplot(data = mean_dist, mapping = aes(x=mean_sd_tibble)) + 
  geom_histogram(bins=100) +
  theme_bw()
```
### Question: 7
```{r Ex_2_Q7, message=FALSE, warning=FALSE}
```
**Answer:**
Both the mean and sd plots of the population looks normally distributed.

### Question: 8
```{r Ex_2_Q8, message=FALSE, warning=FALSE}
# Repeat Question 4 with sample size = 300
mean_samp_300 <- rep(NA, 10000) 

mean_sd_300 <- rep(NA, 10000)
for (i in 1:10000) {
g_samp_300 <- gamma_samp %>% 
  sample_n(300, replace = TRUE) 
mean_samp_300[i] <- mean(g_samp_300$x)
mean_sd_300[i] <- sd(g_samp_300$x)
}
# tibbles for mean_samp and mead_sd
mean_samp_tibble_300 <- tibble(mean_samp_300)
mean_sd_tibble_300 <- tibble(mean_sd_300)
mean_dist_300 <- bind_cols(mean_samp_tibble_300,mean_sd_tibble_300)
# display the sample of final vector
head(mean_dist_300)

# plot for the means_300
ggplot(data = mean_dist_300, mapping = aes(x=mean_samp_tibble_300)) + 
  geom_histogram(bins=100) +
  theme_bw()

# Repeat Question 6 with sample size = 300

# below are sample of the standard deviations of the population
head(mean_sd_tibble_300)

# plot for the standard deviation
ggplot(data = mean_dist_300, mapping = aes(x=mean_sd_tibble_300)) + 
  geom_histogram(bins=100) +
  theme_bw()
```

**Answer:**
Even with the sample size of 300, the distributions of means and sd are looking normally distributed to me. 





