---
title: "COMPSCIX 415.2 Homework 3"
author: "Santosh Kanutala"
date: "6/22/2018"
output:  
  html_document: 
    df_print: paged
  pdf_document: default
  self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## **My Github repository for my assignments can be found at below URL:       (https://github.com/santumagic/compscix-415-2assignments.git)**


```{r load_packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(mdsr)
```
## Section 3.8.1: all excercises

### **QUESTION 1:**

```{r Section 3.8.1_question_1, warning=FALSE, message=FALSE}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()

```


### **ANSWER:**

From the mpg dataset we know that cty and hwy both are continuous variables and when we plot them in a single plot, many data points will be overlapped especially for larger datasets. We can resolve this issue (overplotting) by using adjustment to jitter with position = "jitter" or by using geom_jitter () as shown below.  
 

ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point() + 
  geom_jitter()
  
  
### **QUESTION 2:**

### **ANSWER:**
##Lets find from the help function.

```{r Section 3.8.1_question_2, warning=FALSE, message=FALSE}
?geom_jitter
```
width and hight are the parameters that control the jittering.

### **QUESTION 3:**

### **ANSWER:**

```{r Section 3.8.1_question_3, warning=FALSE, message=FALSE}
# geom_jitter()
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point() + 
  geom_jitter()

# geom_count()
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point() + 
  geom_count()
```
geom_count() is varient of geom_point and it basically it counts the number of data elements or observations at a point in the plot and then maps that count to the pointing area.

### **QUESTION 4:**

### **ANSWER:**

By observing all the below graphs, we can conclude that **position = "dodge"** is the default position adjustment for a boxplot.



```{r Section 3.8.1_question_4, warning=FALSE, message=FALSE}
ggplot(data = mpg, mapping = aes(x = class, y = hwy, color = drv)) + 
  geom_boxplot()

# lets try all types of position adjustments

# position = "Identity"
ggplot(data = mpg, mapping = aes(x = class, y = hwy, color = drv)) + 
  geom_boxplot(position = "Identity")
  
# position = "dodge"
ggplot(data = mpg, mapping = aes(x = class, y = hwy, color = drv)) + 
  geom_boxplot (position = "dodge")

# position = "jitter"
ggplot(data = mpg, mapping = aes(x = class, y = hwy, color = drv)) + 
  geom_boxplot (position = "jitter")

# position = "fill"
ggplot(data = mpg, mapping = aes(x = class, y = hwy, color = drv)) + 
  geom_boxplot (position = "fill")

```


## Section 3.9.1: #2 and #4 only

### **QUESTION 2:**


```{r Section 3.9.1_question_2, warning=FALSE, message=FALSE}
?labs ()
```

### **ANSWER:**

labs will changes the lables for the axes. In addition we can use this for titles and substitles aswell.


### **QUESTION 4:**


```{r Section 3.9.1_question_4, warning=FALSE, message=FALSE}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point() + 
  geom_abline() + 
  coord_fixed()

```

### **ANSWER:**

-- From the above graph it is observed that the both the variables are positively related to each other.  
-- coord_fixed is important because it is making sure that the coordinates for the both variables are fixed.  
-- geom_abline plots the slope between the variables cty and hwy.


## Section 4.4: #1 and #2 only

### **QUESTION 1:**

my_variable <- 10
my_var1able


### **ANSWER:**

There is a type in the second line. It should be : my_variable

### **QUESTION 2:**

### **ANSWER:**

ggplot(data = mpg) + 
  geom_point(mapping = aes(x =displ, y = hwy))

filter(mpg, cyl == 8)  
filter(diamonds, carat > 3)
































