---
title: "homework_7_kanutala_santosh"
author: "Santosh Kanutala"
date: "7/22/2018"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    highlight: tango
  html_document:
    highlight: tango
    number_sections: no
    theme: readable
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\newpage
## <u>Github location</u>
My homework assignments can be found at   https://github.com/santumagic/compscix-415-2assignments.git

## <u>Exercise 1</u>
```{r load_packages, message=FALSE, warning=FALSE}
# Load the required packages
library(tidyverse)
library(mdsr)
```
```{r Ex_1, message=FALSE, warning=FALSE}
# Load the train.csv file
homes <- read.csv ("/Users/skanutal/Documents/Santosh/Learning/Berkeley/3. Intro to DS/Assignments/train.csv", sep = "," )
# glimpse the data from the final csv file
glimpse(homes)
```

**Answer:**
There are 81 variables, and 1460 observations

## <u>Exercise 2</u>
```{r Ex_2, message=FALSE, warning=FALSE, fig.align='center'}

# Install the required pacages and load them
# install.packages("broom") # commented to not to run each time
library(broom)

# Histogram for the distribution of SalePrice
ggplot(data = homes) +
  geom_histogram(mapping = aes(x = SalePrice), binwidth = 10000) + 
  labs (x = 'Sale Prices of homes', y = 'Count', title = 'Sales price of homes by count') +
  theme_bw()

# Visualize the covariation between SalePrice and Neighborhood
ggplot(homes) +
  geom_point(mapping = aes(x=SalePrice, y = Neighborhood)) + 
  theme_bw()

# Visualize the covariation between SalePrice and OverallQual
ggplot(homes) +
  geom_point(mapping = aes(x=SalePrice, y = OverallQual)) +
  theme_bw()

```


## <u>Exercise 3</u>
```{r Ex_3_Q1, message=FALSE, warning=FALSE, fig.align='center'}
# take a look at the coefficient
homes_simple <- lm(SalePrice ~ 1, data = homes)
tidy(homes_simple)
```

**Answer:**
The coefficient is: 180921.2

```{r Ex_3_Q2, message=FALSE, warning=FALSE, fig.align='center'}
# compare the coefficient to the average value of SalePrice
homes_avg_val <- mean(homes$SalePrice)
homes_avg_val
```

**Answer:**
The average value of the sale price from the train data set is equal to the coefficient and is equal to 180921.2

```{r Ex_3_Q3, message=FALSE, warning=FALSE, fig.align='center'}
# take a look at the R-squared
glance(homes_simple)
```

## <u>Exercise 4</u>
```{r Ex_4_Q1, message=FALSE, warning=FALSE, fig.align='center'}
# take a look at the GrLivArea & OverallQual cooefficients
homes_lm <- lm(formula = SalePrice ~ GrLivArea + OverallQual + Neighborhood, data = homes)
tidy(homes_lm)
summary(homes_lm)
```

**Answer:**
Coefficient of GrLivArea = 55.56 & Coefficient of OverallQual = 20951.42. This means that increase in sales price is proportional these cooefficients.

```{r Ex_4_Q2, message=FALSE, warning=FALSE, fig.align='center'}
# take a look at the NeighborhoodBrkSide coefficient
```
**Answer:**
From the summary of above question, it is noted that coeﬃcient of NeighborhoodBrkSide is -13025.45.  
For every unit increase in NeighborhoodBrkSide the SalePrice would decrease by 13025.45.

```{r Ex_4_Q3, message=FALSE, warning=FALSE, fig.align='center'}
# Are the features significant?
```
**Answer:**
Yes the features are significant and linear in nature.

```{r Ex_4_Q4, message=FALSE, warning=FALSE, fig.align='center'}
# Are the features practically significant?
```
**Answer:**
I think yes, all the listed features are practically significant. But potential home buyer can think of many other situations as well apart from these features.

```{r Ex_4_Q5, message=FALSE, warning=FALSE, fig.align='center'}
# Are the features practically significant?
```
**Answer:**
With an Adjusted R-squared value of 0.783, the model seams to be a good fit for the given data.









