---
title: "COMPSCIX 415.2 Homework 2"
author: "**Santosh Kanutala**"
date: "6/13/2018"
output:
  pdf_document: default
  html_document: 
    df_print: paged
  self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **My Github repository for my assignments can be found below URL:                      (https://github.com/santumagic/compscix-415-2assignments.git)**

```{r load_packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(mdsr)
```

## **Section 3.2.4: Excercises**

## **Question 1:**

```{r, message=FALSE, warning=FALSE}
ggplot(data = mpg)

```

##**Answer:** 

From the above function, I see a blank graph, which is a coordinate system.


## **Question 2:**

```{r, message=FALSE, warning=FALSE}
glimpse(mpg)

```

##**Answer:**

There are 234 rows (observations) and 11 columns (varibles).


## **Question 3:**

```{r,}
?mpg
```

##**Answer:**

drv variable describes the drive type of the vehicle like f = front wheel drive, r = rear wheel drive etc. 


## **Question 4:**

```{r, message=FALSE, warning= FALSE}
ggplot(data = mpg) + geom_point(mapping = aes(x = hwy, y = cyl))

```

##**Answer:**


## **Question 5:**

```{r, message=FALSE, warning=FALSE}
ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = drv))
```



##**Answer:**

The graph is not useful because there is no clear relation between drv and class of a vehicle. For example, there are no front wheel and rear wheel drive types are 2 seater vehicles.