---
title: "COMPSCIX 415.2 Homework 2"
author: "**Santosh Kanutala**"
date: "6/13/2018"
output:
  pdf_document: default
  html_document: 
    df_print: paged
  self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **My Github repository for my assignments can be found below URL:                      (https://github.com/santumagic/compscix-415-2assignments.git)**

```{r load_packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(mdsr)
```

## **Section 3.2.4: all excercises**

## **Question 1:**

```{r, message=FALSE, warning=FALSE}
ggplot(data = mpg)

```

##**Answer:** 

From the above function, I see a blank graph, which is a coordinate system.


## **Question 2:**

```{r, message=FALSE, warning=FALSE}
glimpse(mpg)

```

##**Answer:**

There are 234 rows (observations) and 11 columns (varibles).


## **Question 3:**

```{r,}
?mpg
```

##**Answer:**

drv variable describes the drive type of the vehicle like f = front wheel drive, r = rear wheel drive etc. 


## **Question 4:**

```{r, message=FALSE, warning= FALSE}
ggplot(data = mpg) + geom_point(mapping = aes(x = hwy, y = cyl))

```



## **Question 5:**

```{r, message=FALSE, warning=FALSE}
ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = drv))
```

##**Answer:**

The graph is not useful because there is no clear relation between drv and class of a vehicle. For example, there are no front wheel and rear wheel drive types are 2 seater vehicles.


## **Section 3.3.1: all excercises**

## **Question 1:**

```{r, warning=FALSE, message=FALSE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))

```
##**Answer:**

In the above code we are trying to map the three aesthetics x, y, color to three variables of the dataset. But for the third aesthtic is assigned as a text "blue" same as displ and hwy. But we can manually override the color by placing the level outside of aes as shown below.


```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy), color = "blue")

```



## **Question 2:**

```{r, warning=FALSE, message=FALSE}
?mpg
```

##**Answer:**

By looking at the above sample data, I can devide the variables as below.

###**Categorical**
manufacturer  
model  
cyl  
trans  
drv  
fl  
class  

###**Continuous**
displ  
year  
cty  
hwy  


## **Question 3:**

```{r, message=FALSE, warning=FALSE}
 
## Mapping to Continuous Variables
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = year))
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, size = year))
## ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, shape = year))

## Mapping to discrete Variables
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, size = class))

```

##**Answer:**

##** Mapping to Continuous Variables**  

I have mapped the aesthetics color, size and shape to a coontinuous variable "year" and following are my observations.

When I mapped year to color, years are plotted with gradient colors on the map.  
When I mapped year to size, years are plotted with different sizes and in this plot exact size of the point will explain the model years.  
We can't map a continuous variable like year to shape aesthetic because shapes can't be ordered.

##** Mapping to categorical Variables**

When we map an aesthetic to a categorical variable, category names are plotted insted of the scale.
 
## **Question 4:**

```{r, message=FALSE, warning=FALSE}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = year, size = year))


```

##**Answer:**

When we use a variable to map it to multiple aesthetics, simply two layers will be plotted on the same plot as shown above.

## **Question 5:**

```{r, warning=FALSE, message=FALSE}
?geom_point

## Example by using stoke aesthetic

ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, storke = cty), shape = 24)


```

##**Answer:**

stroke aestheric controls the width of the border for any shapes with borders.

## **Question 6:**

```{r, warning=FALSE, message=FALSE}
ggplot(data = mpg) + geom_point(mapping = aes(x = hwy, y = cty, colour = displ < 5))

```


##**Answer:**

When we map an aesthetic like colour to displ < 5, ggplot will takes it as an expression and maps that to True or False to the colour argument.
