---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "Santosh Kanutala"
date: "7/6/2018"
output:
  html_document:
    highlight: tango
    number_sections: no
    theme: readable
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: 3
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Github location
My homework assignments can be found at   https://github.com/santumagic/compscix-415-2assignments.git

## RStudio and R Markdown
+ ### Question: 1
As part of this question, I have loaded the required packages and added instructions for table of contents etc in the YAML header.
```{r load_packages, message=FALSE, warning=FALSE}
# Load the required packages
library(tidyverse)
library(mdsr)
library(nycflights13)
```
## The tidyverse packages
+ ### Question: 1
Plotting - **ggplot2**  
Data munging/wrangling - **dplyr** and **tidyr**  
Reshaping (speading and gathering) data - **tidyr**  
Importing/exporting data - **readr**  

+ ### Question: 2
Plotting - **ggplot()** and **aes()**  
Data munging/wrangling - **select()** and **filter()**    
Reshaping (speading and gathering) data - **separate()** and **extract()**  
Importing/exporting data - **read_csv()** and **read_delim()**   

## R Basics
+ ### Question: 1
```{r R Basics_Q1, warning=FALSE, message=FALSE}
My_data.name___is.too00ooLong <- c( 1 , 2 , 3 )
```
**Answer:** Just with one change (removal of '!'), the code works.  

+ ### Question: 2
```{r R Basics_Q2, warning=FALSE, message=FALSE}
# this is a charactor vector
my_string <- c('has', 'an', 'error', 'in', 'it')
my_string
```
+ ### Question: 3
```{r R Basics_Q3, warning=FALSE, message=FALSE}
my_vector <- c(1, 2, '3', '4', 5)
my_vector
```
**Answer:** This is a numeric vector and with or without the single or double quotes, vactor takes values.  

## Data import/export
+ ### Question: 1
```{r R Data import/export_Q1, warning=FALSE, message=FALSE}
# Download and import the file rail_trail.txt
rail_trail.txt <- read.delim("/Users/skanutal/Documents/Santosh/Learning/Berkeley/rail_trail.txt", sep="|")
#glimpse the data from txt file
glimpse(rail_trail.txt)
```
+ ### Question: 2
```{r R Data import/export_Q2, warning=FALSE, message=FALSE}
# Export the .txt file as csv into a different location
rail_trail_csv <- write_delim(
  rail_trail.txt, delim = '|',path = "/Users/skanutal/Documents/Santosh/Learning/Berkeley/3. Intro to DS/Assignments/rail_trail.csv"
  )
# Load the newly created csv file
rail_trail_csv_final <- read.csv(
  "/Users/skanutal/Documents/Santosh/Learning/Berkeley/3. Intro to DS/Assignments/rail_trail.csv", sep="|"
  )
# glimpse the data from the final csv file
glimpse(rail_trail_csv_final)
```

## Visualization
+ ### Question: 1
```{r}

```
+ ### Question: 2
```{r}

```
+ ### Question: 3
```{r}

```
## Data munging and wrangling

### Question: 1

### Question: 2

### Question: 3

## EDA

### Question: 1

### Question: 2

### Question: 3

### Question: 4

### Question: 5

### Question: 6

## Git and Github








