---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "Santosh Kanutala"
date: "7/5/2018"
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
  html_document:
    highlight: tango
    number_sections: no
    theme: united
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Github location
My homework assignments can be found at   https://github.com/santumagic/compscix-415-2assignments.git

## RStudio and R Markdown
### Question: 1
As part of this question, I have loaded the required packages and added instructions for table of contents etc in the YAML header.
```{r load_packages, message=FALSE, warning=FALSE}
# Load the required packages
library(tidyverse)
library(mdsr)
library(nycflights13)
```

## The tidyverse packages
Plotting - **ggplot2**  
Data munging/wrangling - **dplyr** and **tidyr**  
Reshaping (speading and gathering) data - **tidyr**  
Importing/exporting data - **readr**  

### Question: 1

### Question: 2

## R Basics

### Question: 1

### Question: 2

### Question: 3

## Data import/export

### Question: 1

### Question: 2

## Visualization

### Question: 1

### Question: 2

### Question: 3

## Data munging and wrangling

### Question: 1

### Question: 2

### Question: 3

## EDA

### Question: 1

### Question: 2

### Question: 3

### Question: 4

### Question: 5

### Question: 6

## Git and Github








